Transfer report

### 2018-10-28 Report/paper-results.Rmd
changes how tukey reporting works

@@

Mixed effect models with individual random effect show significant effect of the of the learning condition on rate of improvement from pre-switch to post-switch block (See table XXX ).

@@

Tukey post-hoc tests show significant difference between error rate improvement between the group that learned in the real world and that which learned on the desktop.
```{r, echo=F}
kable(tukey_report(TukeyHSD(x=aov(block34 ~ learning.condition, df_wide_errors), conf.level=0.95)$learning.condition[, c(1,4)]))
```

@@

### Something about pointing?

>>>>

**Running the tukey on these???**
There was also a difference between conditions in their pointing performance at the end of the first phase (`r apa_print(aov(abs_error ~ learning.condition, data = sub_sop_all))$statistic$learning_condition`), with both Treadmill VR group and the Desktop group performend significantly worse than the group in the real world.
```{r}
TukeyHSD(aov(abs_error ~ learning.condition, data = sub_sop_all))
```

@@

Mixed effect models with individual random effect show significant effect of the of the learning condition on rate of improvement from pre-switch to post-switch block (See table XXX).

@@

Tukey post-hoc tests show significant difference between error rate improvement between the group that learned in the real world and that which learned on the desktop.
```{r, echo=F}
kable(tukey_report_table(TukeyHSD(x=aov(block34 ~ learning.condition, df_wide_errors), conf.level=0.95), "learning.condition"))
```

@@

### Something about pointing?
```{r}
err_phase <- lmer(abs_error ~ phase*learning.condition + (1 | id/phase), data = sub_sop_all)
car::Anova(err_phase, type = "III")

ggplot(sub_sop_all, aes(phase, abs_error, color = learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.5, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1.25, geom="line")

aov(abs_error ~ learning.condition, data = sub_sop_all)
```

### 2018-10-28 Report/paper-story.Rmd
changes how tukey reporting works

```{r, echo=F}
df_temp <- TukeyHSD(x=aov(min_norm_distance ~ learning.condition, sub_walk_all[sub_walk_all$phase == 2,]), conf.level=0.95)$learning.condition[, c(1,4)]
kable(tukey_report(df_temp))
```

@@

Post hoc tests show significant difference between Real and Desktop and marginally for Treadmill and Desktop.
```{r, echo=F}
kable(tukey_report(TukeyHSD(x=aov(block34 ~ learning.condition, df_wide_errors), conf.level=0.95)$learning.condition[, c(1,4)]))
```

@@

```{r, echo=F}
kable(tukey_report(TukeyHSD(x=aov(block14 ~ learning.condition, df_wide_errors), conf.level=0.95)$learning.condition[, c(1,4)]))
```

>>>>

```{r, echo=F}
df_temp <- TukeyHSD(x=aov(min_norm_distance ~ learning.condition, sub_walk_all[sub_walk_all$phase == 2,]), conf.level=0.95)
kable(tukey_report_table(df_temp,"learning.condition"))
```

@@

Post hoc tests show significant difference between Real and Desktop and marginally for Treadmill and Desktop.
```{r, echo=F}
kable(tukey_report_table(TukeyHSD(x=aov(block34 ~ learning.condition, df_wide_errors), conf.level=0.95),"learning.condition"))
```

@@

```{r, echo=F}
kable(tukey_report_table(TukeyHSD(x=aov(block14 ~ learning.condition, df_wide_errors), conf.level=0.95),"learning.condition"))
```
